\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{hyperref}% http://ctan.org/pkg/hyperref
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	urlcolor=blue
}

\begin{document}
	
	\noindent
	\textbf{\Large{Erd\H{o}s} Institute C\H{o}de Boot Camp Prerequisite Materials}
	
	\vspace{4mm}
	\noindent
	This folder contains a number of jupyter notebooks that review the minimum knowledge we are asking participants to have. Each notebook will provide a quick review. Students can also test their skills in each topic with the corresponding skill check notebook.
	
	\vspace{2mm}
	\noindent
	Note that Probability and Statistics will not have a jupyter notebook, but rather a 7 page ``cheat sheet'' with core concepts from Probability Theory and Statistics. You by no means need to be an expert in probability theory or statistics, but you should have a passing familiarity with the topics presented in the cheat sheet. In lieu of a Skill Check notebook you can practice the problems provided here:
	
	\noindent
	\href{https://www.math.kth.se/matstat/gru/sf1901/TCOMK/exercises.pdf}{https://www.math.kth.se/matstat/gru/sf1901/TCOMK/exercises.pdf}. 
	
	\noindent
	You don't need to be able to solve all of the problems at the link, they're just offered as a way for you to practice with answers. Also note that the link was not produced by the boot camp, but was found with a quick Google search.
	
	\vspace{2mm}
	\noindent
	These materials should be completed in the following order.
	\begin{enumerate}
		\item Start Here! - My First Jupyter Notebook
		\item Python Basics
		\item pandas
		\item numpy
		\item Basic Plotting matplotlib
		\item Probability and Statistics
	\end{enumerate}
	
	\vspace{2mm}
	\noindent	
	We are giving you the materials well in advance of the boot camp start date. Trying to cover everything we've presented here in a short amount of time can be quite overwhelming, especially if you're brand new to python. Be sure to take your time and don't get discouraged, you can do it!
	
\end{document}